\documentclass[letter,12pt]{article}

\include{cv-commands}

\begin{document}

\header
{Yang WenTao}
{yangwentao@bytedance.com \\ (+86)151-2280-1687}
{Tianjin University\\
Bytedance.Inc}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{statementblock}{Job Objective}
	I'm looking for a job as a TikTok's backend architect, and I'm especially skilled in recommendation systems, especially in the position related to feature engineering.
\bigskip
\end{statementblock}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{resumeblock}{Education}

\resumeitem{Bachelor of Studies}
{{Software Engineering}, Sept. 2013 - June 2016(Expected), {Tianjin University}
}

\end{resumeblock}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{resumeblock}{Skills}
 
\resumeitem{Knowledge}{Algorithm and Data Structure\experiencemost, Performance Optimization\experiencemid,Feature Engineering\experiencelow.}

\resumeitem{Language}{C++/C\experiencemost, Python\experiencemid, Java,Go\experiencelow}


\end{resumeblock}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{resumeblock}{Awards}

\resumeitem{2017 and 2023}{Won the company's Spot Bonus.}



\end{resumeblock}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{resumeblock}{Projects}

\resumeitem{Feature engineering}{responsible for covering the feature engineering of the recommendation scenario, including feature consumption, feature backtracking, platform monitoring, cost governance, etc. Based on the feature elimination lossless optimization, tens of thousands of nuclear resources online were eliminated, and it was promoted to most of the major internal businesses of ByteDance for use.}

\resumeitem{Sorting module}{responsible for the online stability and performance optimization of the company's recommendation system fine-sorting module. With many online optimization methods, the resource cost performance of the fine-sorting module continued to increase during my tenure, supporting the rapid growth of the business.}

\end{resumeblock}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{resumeblock}{Projects}

\resumeitem{-}{Reliable and hard-working. There was a response to everything, and everything was settled.}

\resumeitem{-}{Has a global perspective and can break down complex problems into multiple simple ones}

\resumeitem{-}{Constantly challenges oneself and has good resilience.}


	
\end{resumeblock}

\end{document}
